Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
MUSES API and MUSES Aware apps are now better explained. Related to #33. Please review before closing

The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between MUSES client and MUSES server. 
In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring with the sensors and acting as a consequence of the decisions made by the system). This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}. 
Some of the commented sensors require the interaction with MUSES Aware Apps, in order to request for information. For instance, the MAIL SENSOR could not detect or recognize the contents of an e-mail unless the mail application provides them (so this must be MUSES Aware).

>>>>

The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager}, which controls the communications between MUSES client and MUSES server. 
In addition, there are two types of applications considered in this system. On the one hand, the \textit{MUSES Aware App} is an application adapted to MUSES, so the system can directly interacts with it. This application must be implemented using the MUSES API (Application Program Interface). It should be noted that MUSES is an application that is running in the background, and third party apps can communicate with MUSES and ask for a response. Then, the MUSES API is not a normal API for building the third party application, but a collection of methods to allow this communication\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
The main advantage of having MUSES Aware applications, is because actuator is able to actually forbid the users for doing something, if it implies a big risk for the company.
